### 2021-10-13 plos_latex_template.tex
Rocío: Shortening rule 2

% Rocío: Main message of the paragraph: Why we are writing this piece
Conferences are spaces to meet and reconnect with members from a specific community, learn about advances in the field, and share our recent contributions. 
However, conferences are likely to reproduce the systematic discrimination occurring in other spaces in our fields.
An exclusionary conference experience can divert career paths, affect lives, and drive people out of academia \cite{biggsAcademicConferenceChilly2018}.
Efforts to address systematic discrimination in conferences and make them inclusive spaces can have a meaningful impact on our communities and the lives and careers of their members.

@@

% Rocío: more effort towards including the more excluded
Recognizing our privileges--unearned advantages given by society to some people but not all--particularly in our field and in our scientific or professional community, will help identify which subgroups have been the most excluded or discriminated against. 
These are the groups we need to make more effort to include. 
Investing more effort in the most excluded groups does not mean neglecting the others (see \textbf{Rule \ref{rule_inclusion}} for more on that), but it will guide the vision of diversity for your conference--and your strategies to achieve it:
Will a more diverse conference translate into an even gender distribution in your speakers? 
Would it be the presence of racialized people --especially Black people-- among the head organizers, speakers, and attendees? 
Would it be having LGBTQIA+ friendly-spaces or community participation from key geographic regions?
Depending on the field, region, or community, it could be Black people, LGBTQIA+, Muslim, or other people.
Intersectionality, or the complex, cumulative way in which the effects of multiple forms of discrimination combine or intersect, should be taken into account. 
% This exercise will also help coming up with indicators that would help the organizing team assess the fulfillment of the diversity objectives along the way.

@@

While it is essential to improve representation towards some of the most visible dimensions of human diversity, such as race, gender, and country of origin, building a truly inclusive environment means taking care of all the other aspects of diversity as well. Having consideration of religious practices, setting specific accommodations for breastfeeding and child care, having LGBTQIA+-friendly spaces, creating community-only spaces, enforcing the use of pronouns, and acknowledging that gender is not binary are just some examples of decisions that can make inclusion real.
Importantly, you can take active steps in creating a more welcoming environment without requiring anyone to disclose personal information.

Paying attention to some dimensions of diversity while neglecting others may have unintended, even harmful consequences. Lack of representation, unwelcoming--or overtly aggressive-- environments hinder participation (or future participation) of people who could otherwise become active community members. A negative conference experience can divert career paths, affect lives, and exclude people from some fields \cite{biggsAcademicConferenceChilly2018}. 
%ast maybe this last sentence could go in the introduction because it's general i marked [bad experience] in the intro

Adopting a code of conduct and creating a team to enforce it are key aspects in creating a safe environment during a conference \cite{favaroYourScienceConference2016}.
The code of conduct is a document meant to keep the community safe and should state clearly: the unacceptable behaviors, the spaces of the conference in which it applies, the consequences for engaging in unacceptable behavior, and the way to report violations \cite{auroraHowRespondCode2019}. 
The code of conduct should be displayed prominently in several spaces of the conference to deter people from unacceptable behavior.
An efficient code of conduct acts as a protection for the community because the people who are the target of unacceptable behavior tend to be the ones with less power or privilege.

The code of conduct team should receive training on how to receive reports, respond to incidents, and communicate their responses, and organize accordingly. A diverse code of conduct team will be more understanding of power dynamics and sensitive to discrimination and harassment issues. There are also disciplinary cultures and geographical considerations that may need to be considered when developing and communicating the code of conduct (CoC). We strongly recommend reading `How to Respond to Code of Conduct Reports' \cite{auroraHowRespondCode2019} as an excellent starting point for the Code of Conduct teamwork.

>>>>

% Rocío: Main message of the paragraph: Why we are writing this piece
Conferences are spaces to meet and reconnect with members from a specific community, learn about advances in the field, and share our recent contributions. 
However, conferences are likely to reproduce the systematic discrimination occurring in other spaces in our fields.
Lack of representation and unwelcoming--or overtly aggressive--environments hinder participation (or future participation) of people who could otherwise become active community members. 
An exclusionary conference experience can divert career paths, affect lives, and drive people out of academia \cite{biggsAcademicConferenceChilly2018}.
Efforts to address systematic discrimination in conferences and make them inclusive spaces can have a meaningful impact on our communities and the lives and careers of their members.

@@

% Rocío: more effort towards including the more excluded
Recognizing our privileges--unearned advantages given by society to some people but not all--particularly in our field and in our scientific or professional community, will help identify which subgroups have been the most excluded or discriminated against. 
These are the groups we need to make more effort to include. 
Investing more effort in the most excluded groups does not mean neglecting the others, but it will guide the vision of diversity for your conference--and your strategies to achieve it:
Will a more diverse conference translate into an even gender distribution in your speakers? 
Would it be the presence of racialized people --especially Black people-- among the head organizers, speakers, and attendees? 
Would it be having LGBTQIA+ friendly-spaces or community participation from key geographic regions?
Depending on the field, region, or community, it could be Black people, LGBTQIA+, Muslim, or other people.
Intersectionality, or the complex, cumulative way in which the effects of multiple forms of discrimination combine or intersect, should be taken into account. 
% This exercise will also help coming up with indicators that would help the organizing team assess the fulfillment of the diversity objectives along the way.

@@

% Rocío: main idea: Inclusion for everyone
While it is essential to improve representation towards some of the most visible dimensions of human diversity, such as race, gender, and country of origin, building a truly inclusive environment means taking care of all the other aspects of diversity as well. 
Having consideration of religious practices, setting specific accommodations for breastfeeding and child care, having LGBTQIA+-friendly spaces, creating community-only spaces, and acknowledging that gender is not binary are just some examples of decisions that can make inclusion real.
Importantly, you can take active steps in creating a more welcoming environment without requiring anyone to disclose personal information.

% Rocío: main idea: Code of conduct for a safe place
Adopting a code of conduct and creating a team to enforce it are key aspects in creating a safe environment during a conference \cite{favaroYourScienceConference2016}.
The code of conduct is a document meant to keep the community safe and should state clearly the unacceptable behaviors, the consequences for engaging in such behavior, and the way to report violations \cite{auroraHowRespondCode2019}. 
The code of conduct team should receive training on how to receive reports, respond to incidents, and communicate their responses, and organize accordingly. 
A diverse code of conduct team will be more understanding of power dynamics and sensitive to discrimination and harassment issues. 
There are also disciplinary cultures and geographical considerations that may need to be considered when developing and communicating the code of conduct. 
We strongly recommend reading `How to Respond to Code of Conduct Reports' \cite{auroraHowRespondCode2019} as an excellent starting point for the Code of Conduct teamwork.
% Rocío: two of these sentences, diverse CoC team, and communication of CoC, may belong to rules organizing team and communication, respectively.

% Rocío: Could have a paragraph about active bystandership—Andrea
